Interval Probability for Fuzzy Quantum Theories

### 2016-06-14 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} updates...

If we adopt the frequency interpretation as in section~\ref{subsec:Measuring-Probabilities:-Buffon},
and measure the angular momentum for a spin-one particle in the Stern-Gerlach
experiment~\cite{FeynmanLeightonSands1965,Stern1988,peres1995quantum,544199}.
Ideally, if the local field strength directs to the $z$-axis, and
all particles have the same velocity, three spots will be produced
corresponding to $\ket{+Z}$, $\ket{0Z}$, and $\ket{-Z}$. In reality,
the local field strength cannot prefect directs to to the $z$-axis,
and all particles come from a hot oven cannot have the same velocity.
As the result, spots will be broader and more washed out so that it
may sometimes hard to decide a particle corresponding to which state\footnote{\yutsung{Citation here?}}.
Similar to Buffon's needles, this kind of fuzziness can be taken into
account by associating each quantum event with an interval-valued
probability~$\left[l,r\right]$. About the imperfect direction of
field strength, we might take it into account when we introduce the
discrete quantum theory later.

@@

%%%%%
\subsection{Quantum Interval-valued Probabilities Measures}

>>>>

Similar to the classical case, by applying the law of large number,
quantum probabilities can be estimated by relative frequencies as
well.. For example, Stern and Gerlach found a beam of silver atoms
deflects in a highly inhomogeneous magnetic field~\cite{Stern1988,peres1995quantum,544199,Griffiths2003}.
Ideally, if the local field strength directs to the $z$-axis, and
all particles have the same velocity, two spots will be produced corresponding
to $\ket{0}$ and $\ket{1}$. In reality, we need a lot of resource
to keep the local field of strength directing to the $z$-axis, to
keep the atoms having almost the same velocity, and to point out the
exact position each particle landed on.

If the field of strength does not perfectly direct to the $z$-axis,
we does not really test the quantum event we want to test. This problem
will be handled later when we introduce the discrete quantum theory.
Even if the field of strength is perfectly direct to the $z$-axis,
the variant velocity makes spots broader and more washed out. Together
with the precision limit of the detector, it may sometimes be hard
to decide a particle corresponding to which state. For higher spins,
the bounded resource even limits the ability of entangled systems
to exhibit the violation of Bell's inequalities~\cite{CostaHarriganRudolphEtAl2009}.
Similar to Buffon's needles, this kind of fuzziness can be taken into
account by associating each quantum event with an interval-valued
probability~$\left[l,r\right]$.

@@

%%%%%

\subsection{Quantum Interval-valued Probabilities Measures}

As mentioned above, each quantum event~$P$ will be associated with
an interval-valued probability~$\left[l,r\right]$. Notice that whenever
the magnetic field of the Stern-Gerlach is fixed, i.e., an complete
set of orthogonal projections are picked, measuring the spin is up
or down is exactly the same as tossing a coin. In another word, if
somebody claimed she is tossing a coin behind a veil, and only show
the resulting heads or tails, we cannot distinguish whether she has
really tossed a coin, or she has run an Stern-Gerlach experiment,
and show us the head, the tail, or the side of coin if the silver
atoms is spin up, spin down, or just hit the middle. Therefore, applying
interval

\begin{definition}[Quantum Interval-valued Probability Measure]\label{def:QuantumInterval-valuedProbability}
Given a Hilbert space $\Hilb$ with the set of quantum events~$\events$,
a \emph{quantum interval-valued probability measure} is a function
$\mu:\events\rightarrow[0,1]$ such that:
\begin{itemize}
\item $\mu(\mathbb{0})=\left[0,0\right]$, 
\item $\mu(\mathbb{1})=\left[1,1\right]$, 
\item $\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathscr{I}}]{-}{}\mu\left(P\right)$,
and 
\item for mutually orthogonal projections $P_{i}$, we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\mu\left(P_{i}\right)$. 
\end{itemize}
\qed\end{definition}
